Assessing the Global COVID19 Impact on Air Transport with Open Data

### 2021-06-21 paper.Rmd
minor correction

#Normalized by the median of the last 3 months
temp2 <- temp1 %>% pivot_longer(cols = 2:5, names_to = "ROUTE", values_to = "FLIGHTS") %>% group_by(ROUTE) %>% mutate(MOVING_MEDIAN = quantile(FLIGHTS[month(DATE) %in% month(last(DATE))-1:month(last(DATE))], probs = 0.5), NORM_FLTS = FLIGHTS/MOVING_MEDIAN)
temp2

>>>>

#Normalized by the median of the last 3 months of the dataset
temp2 <- temp1 %>% pivot_longer(cols = 2:5, names_to = "ROUTE", values_to = "FLIGHTS") %>% group_by(ROUTE) %>% mutate(MOVING_MEDIAN = quantile(FLIGHTS[month(DATE) %in% month(last(DATE))-2:month(last(DATE))], probs = 0.5), NORM_FLTS = FLIGHTS/MOVING_MEDIAN)
temp2
